---
title: "anobj"
output: word_document
---
Progression of the analysis has a certain structure. This stucture might contain trees, circles, loops, etc. Herein we limit the structure to a simple sequence

```{r message=FALSE}
# Common functions
source('func.R')

# Input data
library(readxl)
anobs <- read_excel('../data/anobj.xlsx')

# Structure of sample data
str(anobs)

# Summary of properties
table(anobs$property)

# Initialize the analysis sequence
anobj <- newsq('Analysis object', 'anobs')
```

## Analysis object context

### checkpoints

addCenters: select obs with either equal to ckpt or null ckpt
voidCenters: if ckpt specified remove all not equal to ckpt or null ckpt

```{r}
# Create centers
anobj <- grow(anobj, 'SEQUENCE', depth=2, ckpt='context')

# Apply appropriate seed and partition
anobj <- applySeed(sq=anobj, seed=163)
anobj <- applyPartitioning(anobj, 'mbrp')
anobj
```

## Analysis object detailed view

```{r}

anobj <- grow(anobj, 'GRAPH', attrs=T, vals=T, ckpt='details')
anobj <- applySizing(anobj)
anobj <- applySeed(sq=anobj, seed=747)
anobj

# anobj <- applyAlternation(anobj)
#anobj
```

## Analysis object final view [CKPT=Final]

To illustrate the timeline

```{r}

#anobj <- voidCenter(anobj, c('REPORT','STORAGE'))

```

## Analysis object overview

```{r}

```

