---
title: "Generation"
output:
  word_document: default
---
This is analysis of LD module structure for understanding its loan schedule handling mechanisms

```{r message=FALSE}
library(igraph)

#Common functions
source('func.R')

#Load observations
obs <- read.csv('../data/obs.csv', stringsAsFactors=FALSE)

#Start from the root
ldsch <- asq('LD scheduling overview')
ldsch <- addCenter(ldsch, 'LD.LOANS.AND.DEPOSITS')
ldsch
```

There are too many edges shown and none of them seems useful. Remove these and replace with connections based on record scan

```{r}
#Remove clutter
voidList <- grep('LD', V(ldsch$struct[[1]])$name, invert=TRUE, value=TRUE)
ldsch <- voidCenter(ldsch, voidList)
ldsch

#addCenter(ldsch, 'LD.LOANS.AND.DEPOSITS', scan='LD')

```

We need to scale down to attribute level to understand the structure better. No reason to scale up

```{r}
#scaleDown(ldsch)
```

What can we conclude based on analysis

PS. Demonstration that brute force is not helpful with igraph
```{r}
el <- obs[obs$property=='linkdef', ]

from <- sub('>.*$', '', el$object)
to <- gsub("^[^>]+>\\s*", "", el$object)

plot(graph.data.frame(data.frame(from, to, el$value)))
```

