---
title: "meta"
output:
  word_document: 
    fig_height: 10
    fig_width: 8
    highlight: tango
  html_document:
    fig_height: 8
    fig_width: 10
    highlight: tango
---
Progression of the analysis has a certain structure. This stucture might contain trees, cirles, loops, etc. Herein we limit the structure to a simple sequence

## Observations

```{r message=FALSE}
# Load common structural analysis functions
source('atrf.R')

# TODO: Generate data based on analysis object definition?

# Load analysis data from a spreadsheet
suppressWarnings(library(readxl))
anobs <- read_excel('../data/meta_analysis.xlsx')

# Structure of sample data
str(anobs)

# Summary of properties
table(anobs$property)
```

## Context

Something about the context

```{r}
# Initialize the analysis sequence
meta <- analysis('Analysis entity', 'anobs')

# Generate the structure
meta <- grow(meta, 'SEQUENCE', depth=2)
meta <- void(meta, c('EDGE','VERTEX'))

# Polish the output with appropriate seed and partitioning
meta <- applySeed(sq=meta, seed=163)
meta <- applyPartitioning(meta, 'mbrp')
meta
```

## Detailed view

Something about detailed view

```{r}
# Rearrange the structure
meta <- grow(meta, 'GRAPH', depth=2, attrs=TRUE, vals=TRUE)
meta <- void(meta, c('REPORT','STORAGE'))

# Polish the output with appropriate seed 
meta <- applySeed(sq=meta, seed=986)
meta
```

## Transformation demos

### Center
```{r}
# Source data (observations)
sdata <- browseData(meta)
sdata[sdata$objsrc=='EDGE', ]

# Structure elements (target data)
tdata <- getCenters(meta)
tdata[tdata$name=='EDGE', ]

tdata <- getRelations(meta)
tdata[grepl('EDGE', tdata$name), ]

```

### Grouping
```{r}
# Group GRAPH optional attributes
gmbr <- paste0('GRAPH>', c('sizing', 'sizing2', 'checkpoint',
  'partitioning', 'partitioning2', 'alternation', 'simplicity'))
gmeta <- group(meta, 'GRAPH>optional', gmbr)

# Group VERTEX optional attributes
gmbr <- paste0('VERTEX>', c('size',
  'size2', 'membership', 'membership2', 'contrast'))
gmeta <- group(gmeta, 'VERTEX>optional', gmbr)

# Group EDGE optional attributes
gmbr <- paste0('EDGE>', c('label', 'contrast'))
gmeta <- group(gmeta, 'EDGE>optional', gmbr)

# Apply appropriate seed and autoprint
gmeta <- applySeed(gmeta, 181)
gmeta

```

# Embedding
```{r}
# Identify key steps
summary(gmeta)

# Finalize the grouping branch
sqmain <- c('context', 'details', 'grouping')
signoff(gmeta, thumb_seq=c(5, 8, 12), thumb_narr=sqmain)
```

# Essential properties

### Randomization

```{r}
# Check for appropriate seed
browseSeeds(meta)

# Apply not so good seed
meta <- applySeed(meta, 884)
meta

# Current randomization settings
getSeed(meta)

```

## Layout
```{r}
# Check for appropriate layout (without partitioning as not always supported)
meta <- removePartitioning(meta)
browseLayouts(meta, plot=FALSE)
browseLayouts(meta)

# Apply an alternative layout
meta <- applyLayout(sq=meta, layout='layout_with_lgl')
meta

# Current layout
getLayout(meta)
```

## Theme
```{r}
# Check for available themes
browseThemes(meta)

# Try minimalist theme without adding to sequence
applyTheme(meta, 'minimalist')

# Current theme
getTheme(meta)
```

# Optional properties

## Partitioning
```{r}
meta <- applySeed(meta, 532)

# Check clustering algorithms
browsePartitionings(meta, plot=FALSE)
browsePartitionings(meta)

# Visualize pregiven communities 
browseEntities(meta)[ ,c('object', 'mbrp')]

# Use pregiven partitioning instead
meta <- applyPartitioning(meta, 'mbrp')
meta

# Add another partitioning presentation
meta <- applyPartitioning2(meta, 'mbrp')
meta

# Current partitioning
getPartitionings(meta)

```

## Sizing

```{r}
# Function for size calculation
psz <- function(ang) {
  power_centrality(ang)
}

# Sizes calculated by custom function
psz(meta[[length(meta)]])

# Test sizes calculated by the function
applySizing(meta, 'psz')

# Pregiven sizes
browseEntities(meta)[ ,c('object', 'wt')]

# Apply pregiven sizes
meta <- applySizing(meta, 'wt')
meta

# Current sizing
getSizing(meta)
```

## Alternation
```{r}
# Apply alternation
meta <- applyAlternation(meta)
meta

# Current alternation
getAlternation(meta)

# Remove alternation
meta <- removeAlternation(meta)
meta

# Current alternation
getAlternation(meta)
```

## Simplicity
```{r}
# Simple display of 10 biggest centers
applySimplicity(meta, n=10)
```

# Polishing
```{r}

# Prepare for polishing
meta <- applyLayout(meta, 'layout_with_fr')
meta <- applySeed(meta, 776)
meta

# Try Scaling transformation
doScaling(meta, scaling=3)

# Average number of attributes
c <- getCenters(meta)
nrow(c[c$type=='attribute', ])/nrow(c[c$type=='entity', ])

# Try Symmetry transformation
doSymmetry(meta)

# Initiate Gradient transformation from SEQUENCE entity
meta <- doGradients(meta, 'SEQUENCE')
meta <- applyAlternation(meta)
meta
```

# Highlighting
```{r}
# Vertice coloring by membership prevents highlighting 
meta <- removePartitioning2(meta)

# Highlight link attributes
ida <- grep('id', getCenters(meta)$name, value=TRUE)
meta <- applyHighlight(meta, ida)

meta

```

# Dynamics
```{r}
# Facilitate reproducibility
set.seed(3)

# Generate sequences of 9 steps
n <- 9
steps <- 1:n

# Simulate the assembly sequence
asm <- unlist(lapply(steps, function(x) {
  rep(x, x + 1 + abs(rnorm(1, 0, 2)))
}))
s <- data.frame(cbind(type=rep('assembly', length(asm)), count=asm))

# Simulate the differentiation sequence
dif <- unlist(lapply(steps, function(x) {
  rep(x,  n * (n - x + abs(rnorm(1, 0, 2))))
}))
s <- rbind(s, cbind(type=rep('differentiation', length(dif)), count=dif))

# Output using ggplot2 graphics system
library(ggplot2)

col <-'darkblue'
lt <- 'dashed'
ckpt <- c('baseline', 'checkpoint 1', 'checkpoint 2')

# Build the barplot
ggplot(s, aes(x=count, fill=type)) + stat_count(width=0.8, position='dodge') +
  labs(x='steps', y='number of centers') + theme_grey(base_size=16) +
  theme(legend.position="top", legend.text=element_text(size=16)) +

  # Add checkpoints
  geom_vline(aes(xintercept=0.5), color=col, linetype=lt, size=1) +
  geom_text(aes(x=0.5, label=ckpt[1], y=100), hjust=-0.1, color=col, size=5) +
  geom_vline(aes(xintercept=3.5), color=col, linetype=lt, size=1) +
  geom_text(aes(x=3.5, label=ckpt[2], y=100), hjust=-0.1, color=col, size=5) +
  geom_vline(aes(xintercept=5.5), color=col, linetype=lt, size=1) +
  geom_text(aes(x=5.5, label=ckpt[3], y=100), hjust=-0.1, color=col, size=5)
```
