---
title: "Overview"
output:
  word_document:
    fig_height: 8
    fig_width: 12
    highlight: tango
  html_document: default
---
Frequenty there is a need to replace multiple systems with one new system or replace older version of the system with newer version but vendor supported upgrade is not possible. We call this process migration and illustrate below based on a particular instance of moving from significantly older version of the core banking system to a newer version

We have arranged related data observations in a spreadsheet and build our analysis on that

```{r message=FALSE}
# Load observations
suppressWarnings(library(readxl))
mobsw <- read_excel('../data/migration.xlsx')

# Load transformation functions and initiate the sequence
source('atrf.R')
mov <- analysis('Data Migration Overview', datarefw='mobsw')
```

Light exploration on what not covered in case study exploratory analysis

Note the number of observations and their content sampling

```{r message=FALSE}
str(mobsw[ ,1:(ncol(mobsw)-3)], strict.width='cut', width=70)
```

# Source Data Identification
It seems natural to start from the source data identification. We will categorise the date entities according to their migration method (*mbrp_dataset*) and present a compact overview of the source system. Related entities will be prefixed with *src_*.

A metric is needed for differentiating different entities. Number of records (*wt_numrec*) is not an ideal metric, but in this context can be considered good enough for rough estimations

```{r}
# Create a structure comprised of source centers
e <- browseEntities(mov, ckpt='baseline')$object
mov <- grow(mov, e, depth=0, ckpt='baseline')

# Change the size of vertices to reflect record count
mov <- applySizing(mov, 'wt_numrec')

# Change the color of vertices to reflect the dataset
mov <- applyPartitioning2(mov, 'mbrp_dataset')

# Switch to layout which reflects the data best 
mov <- applyLayout(mov, 'layout_with_dh')
mov
```

# Data extraction
Core banking system migration is a complex process and would be difficult to conduct without having an intermediatate system between source and data systems

The problem with the data is that it is constantly changing and there is only a narrow window for conducting the actual migration. Therefore, it is desirable and possible to identify parts which are less prone to change and load these (so called *static data*) earlier.

Contractual etc. highly time-senstitve data has to be imported similarly, whenever there is sufficient time for its subsequent exporting to target system. On the other hand, it is useful to load also the financial data for simulations before the actual migration

This explains separate checkpoints for static and financial data extraction

```{r}
# Add extracted static entities
e <- browseEntities(mov, ckpt='imp_static')$object
mov <- grow(mov, e, depth=0, ckpt='imp_static')

# Migrate financial data
e <- browseEntities(mov, ckpt='imp_financial')$object
mov <- grow(mov, e, ckpt='imp_financial')

# Divide into sub-systems
mov <- applyPartitioning(mov, 'mbrp_system')

# Group extracted source entities for more compact display
c <- getCenters(mov)

src_stat_mbr <- c[c$membership=='src' & c$membership2=='static','name']
mov <- group(mov, 'src_static', src_stat_mbr)

src_fin_mbr <- c[c$membership=='src' & c$membership2=='financial','name']
mov <- group(mov, 'src_financial', src_fin_mbr)

src_skip_mbr <- c[c$membership=='src' & c$membership2=='skip','name']
mov <- group(mov, 'src_skip', src_skip_mbr)

# Switch to layout which suits for partitioning 
mov <- applyLayout(mov, 'layout_components')
mov
```

# Static and Manual Data Migration
Necessary transformations have to be carried on in the intermediary system and then the static data can be exported into the target system

Target system entities are prefixed with *trg_* for presentational purposes. In reality, the entity is likely named the same in source and target systems

```{r}
e <- browseEntities(mov, ckpt='exp_static_man')$object
mov <- grow(mov, e, ckpt='exp_static_man')

mov
```

Note that also related manually transferrable items have been migrated.

After migration we need to reconcile the data. In case of static data that means simple one-to-one matching of source and target data, but also analysis of the items skipped and verifying correctness of conversions rules

```{r}
e <- browseEntities(mov, ckpt='recon')
mov <- grow(mov, e$object[e$mbrp_dataset=='static'], ckpt='recon')

# Remaining source items can be grouped now
c <- getCenters(mov)

src_man_mbr <- c$name[c$membership=='src' & c$membership2=='manual']
mov <- group(mov, 'src_manual', src_man_mbr)

# Most (except target) static entities can be grouped as well
cs <- c[c$membership2=='static','name']

imp_src_mbr <- grep('^imp_src_', cs, value=TRUE)
mov <- group(mov, 'imp_src_static', imp_src_mbr)

exp_mbr <- grep('^exp_', cs, value=TRUE)
mov <- group(mov, 'exp_static', exp_mbr)

imp_trg_mbr <- grep('^imp_trg_', cs, value=TRUE)
mov <- group(mov, 'imp_trg_static', imp_trg_mbr)

mov
```

# Financial Data Transformation and Migration
Necessary transformations have to be carried on in the intermediary system and then the financial data can be exported into the target system. As this is constantly changing data, it has to reload right before migration

```{r}
e <- browseEntities(mov, ckpt='exp_financial')$object
mov <- grow(mov, e, ckpt='exp_financial')
mov

# Target and some financial entites can now be grouped
c <- getCenters(mov)

trg_man_mbr <- c$name[c$membership=='trg' & c$membership2=='manual']
mov <- group(mov, 'trg_manual', trg_man_mbr)

trg_stat_mbr <- grep('^trg_', c[c$membership2=='static','name'], value=TRUE)
mov <- group(mov, 'trg_static', trg_stat_mbr)

cf <- c[c$membership2=='financial','name']
trg_fin_mbr <- grep('^trg_', cf, value=TRUE)
mov <- group(mov, 'trg_financial', trg_fin_mbr)
exp_fin_mbr <- grep('^exp_', cf, value=TRUE)
mov <- group(mov, 'exp_financial', exp_fin_mbr)

mov
```

# Full reconciliation
Source and target data have to be reconciled. Here we have presented this as separate step, allthough it is likely to have various reconciliation activities before all the data has been migrated, for example after static data export

```{r}
e <- browseEntities(mov, ckpt='recon')
mov <- grow(mov, e$object[e$mbrp_dataset=='financial'], ckpt='recon')

# Group remainining financial items
c <- getCenters(mov)
cf <- c[c$membership2=='financial','name']
ifsrc_mbr <- grep('^imp_src_', cf, value=TRUE)
mov <- group(mov, 'imp_src_financial', ifsrc_mbr)
iftrg_mbr <- grep('^imp_trg_', cf, value=TRUE)
mov <- group(mov, 'imp_trg_financial', iftrg_mbr)

mov
```

# Summary
To conclude we will present an overview of the whole sequence by plotting all the representitive steps in one graph


```{r}
sqm <- c('identification', 'extraction')
sqm <- c(sqm, 'static migration', 'static reconciliation')
sqm <- c(sqm, 'financial migration', 'full reconciliation')
signoff(mov, thumb_seq=c(5, 12, 13, 18, 22, length(mov)), thumb_narr=sqm)
```
