---
title: "SEQUENTIAL BUSINESS ANALYSIS SUPPORT TOOL"
output:
  html_document: 
    fig_height: 8
    fig_width: 10
    highlight: tango
    theme: journal
  word_document:
    fig_height: 10
    fig_width: 8
    highlight: tango
---
```{r echo = FALSE}
suppressWarnings(suppressPackageStartupMessages(library(knitr)))
```
An authoritative source (The BABOK Guide [BABOK_Guide_v3_Member.pdf]) defines business analysis as practice of enabling change in an enterprise by defining needs and recommending solutions that deliver value to stakeholders. Sequential business analysis (SBA) method proposes to clarify these needs and solutions iteratively through sequences of specific analysis steps. This method (explained in more detail elsewhere (*TODO: link*)) is heavily influenced by late Christopher Alexander's architectural theories [NoO] and are expected to facilitate particularly adaptive analyses. As generating of sequences can be very laborious, such analysis process is practically unthinkable without proper support tools. Principles of such tool (the analysis ecosystem) is described below first and then the implemented fundamental sequence steps (transformations). Conduction of analyses is illustrated by the tool usage meta-analysis

# The Analysis Ecosystem
The analysis ecosystem is a collection of observations and R functions for generating sequences of transformations based on them:

```{r}
# Load transformation functions 
# TODO: Split into multiple files and package
source('../wda.R')
source('../obs.R')
```

## Observations
Analyses are based on data suitabily organised as observations. The proposed organisation is expected to be flexible enough for supporting majority of business analysis needs. Observations have the following components:

```{r echo = FALSE}
tbl <- matrix(c('Object', "Things (nested hierarchy levels separated by '>') or links (entities separated by '|') between them", 'OBSERVATION>property, VERTEX>id|OBSERVATION'), nrow = 1) %>%
  rbind(c('Property', 'Entity attribute or object meta-characteristic', 'value, type, mandatoriness')) %>%
  rbind(c('Value', 'Property value', '10, numeric, TRUE')) %>%
  rbind(c('Checkpoint', 'Notional or temporal event of measuring (optional)', 'DISBURSEMENT, 2018-03-03T09:57:10'))

colnames(tbl) <- c('Element', 'Definition', 'Examples')

kable(tbl)
```

### Loading from file
Observations can be gathered into a separate file (with columns as in above table and each row corresponding to an observation) and loaded before initiating the analysis sequence (like in the code snippet below).

```{r}
# Load observations for meta-analysis from the spreadsheet
suppressWarnings(library(readxl))
anobs <- read_excel('../data/meta.xlsx')
head(anobs)

# Initialize the analysis sequence
meta <- analysis('Meta-analysis', obs = 'anobs')
```

### Textual definition
Alternatively, the observations can be added on the fly as part of the transformation. For the latter, compact presentation of observations can be handy:

```{r echo = FALSE}

tbl <- rbind(
  c('O', 'O', 'NA', 'NA', 'O', 'NA', 'NA', 'NA', 'NA'),
  c('O>P', 'O', 'P', 'NA', 'O', 'NA', 'P', 'NA', 'NA'),
  c('O=V', 'O',	'id', 'V', 'O', 'NA', 'id', 'NA', 'V'),
  c('O>P=V', 'O',	'P', 'V', 'O', 'NA', 'P', 'NA', 'V'),
  c('O=V>P=V2', 'O', 'id', 'V', 'O', 'NA', 'id', 'NA', 'V'),
  c('', 'O', 'P', 'V2', 'O', 'NA', 'P', 'NA', 'V2'),
  c('O>P>V=V2', 'O>P', 'V', 'V2', 'O', 'NA', 'P', 'V', 'V'),
  c('O|O2', 'O>id|O2', 'type', 'strong', 'O', 'O2', 'id', 'type', 'strong'),
  c('O>P|O2', 'O>P|O2', 'type', 'strong', 'O', 'O2', 'P', 'type', 'strong'),
  c('O|O2=V', 'O>id|O2', 'type', 'strong', 'O', 'O2', 'id', 'type', 'strong'),
  c('O>P|O2=V', 'O>P|O2', 'type', 'strong', 'O', 'O2', 'P', 'type', 'V'),
  c('O|O2>P2=V', 'O>id|O2', 'type', 'strong', 'O', 'O2', 'id', 'P2', 'V'),
  c('O>P|O2>P2=V', 'O>P|O2', 'type', 'strong', 'O', 'O2', 'P', 'P2', 'V')
)

colnames(tbl) <- c('definition', 'object', 'property', 'value', 'h_ent', 'h_ent2', 'h_attr', 'h_meta', 'h_val')

kable(tbl)
```

*TODO: Illustrate adding of obs from text*

### Converting tables etc. structures

*TODO: Generate meta-data based on analysis object definition... graph vertex and edge?*

*TODO: Illustrate by convering a dataframe to obs, e.g. Observations table*

```{r}

# Generate the structure
meta <- grow(meta, 'OBSERVATION', attrs = TRUE, width = 0)

```

## Sequence
Progression of the analysis has a certain structure. Simple chain of incremental steps is preferable, but trees, circles, loops, etc. are possible as well. Each step  corresponds to a most appropriate (wholeness-extending) transformation

Starts with *analysis* and ends with *signoff*

```{r}
# TODO: Modify layout to keep attributes close to entity

# Polish the output with appropriate seed and partitioning
meta <- grow(meta, 'SEQUENCE', width = 2) %>% applySeed(417) %>% applyPartitioning('mbrp')
```

Checkpoint and instance later:

```{r}
summary(meta)

meta
```

## Structural component

Something about detailed view

* TODO: As similar to UML class diagram as possible (except attributes separately)?*

```{r}
# Rearrange the structure
meta <- grow(meta, 'GRAPH', width=2, attrs=TRUE, vals=TRUE)
meta <- void(meta, c('INFERENCE'))

# Polish the output with appropriate seed 
meta <- applySeed(meta, seed = 725)
meta
```

# Transformations

*TODO: Summary table*

Structure Generation
Essential Global Properties
Optional Global Properties
Creating order
Local Properties

### Center
```{r}
# Source data (observations)
sdata <- browseData(meta)
sdata[sdata$objsrc=='EDGE', ]

# Structure elements (target data)
tdata <- getElements(meta)
tdata[tdata$name=='EDGE', ]

tdata <- getRelations(meta)
tdata[grepl('EDGE', tdata$name), ]

```

### Grouping
```{r}
# Group GRAPH optional attributes
gmbr <- paste0('GRAPH>', c('sizing', 'sizing2', 'checkpoint',
  'partitioning', 'partitioning2', 'alternation', 'simplicity'))
gmeta <- group(meta, 'GRAPH>optional', gmbr)

# Group VERTEX optional attributes
gmbr <- paste0('VERTEX>', c('size',
  'size2', 'membership', 'membership2', 'contrast'))
gmeta <- group(gmeta, 'VERTEX>optional', gmbr)

# Group EDGE optional attributes
gmbr <- paste0('EDGE>', c('label', 'contrast'))
gmeta <- group(gmeta, 'EDGE>optional', gmbr)

# Apply appropriate seed and autoprint
gmeta <- applySeed(gmeta, 181)
gmeta

```

# Embedding
```{r}
# Identify key steps
summary(gmeta)

# Finalize the grouping branch
sqmain <- c('context', 'details', 'grouping')
signoff(gmeta, thumb_seq=c(4, 7, 11), thumb_narr=sqmain)
```

# Essential properties

### Randomization

```{r}
# Check for appropriate seed
browseSeeds(meta)

# Apply not so good seed
meta <- applySeed(meta, 527)
meta

# Current randomization settings
getSeed(meta)

```

## Layout
```{r}
# Check for appropriate layout (without partitioning as not always supported)
meta <- removePartitioning(meta)
browseLayouts(meta, plot=FALSE)
browseLayouts(meta)

# Apply an alternative layout
meta <- applyLayout(sq=meta, layout='layout_with_kk')
meta

# Current layout
getLayout(meta)
```

## Theme
```{r}
# Check for available themes
browseThemes(meta)

# Try minimalist theme without adding to sequence
applyTheme(meta, 'minimalist')

# Current theme
getTheme(meta)
```

# Optional properties

## Partitioning
```{r}
# Check clustering algorithms
browsePartitionings(meta, plot=FALSE)
browsePartitionings(meta)

# Visualize pregiven communities 
browseEntities(meta)[ ,c('object', 'mbrp')]

# Use pregiven partitioning instead
meta <- applyPartitioning(meta, 'mbrp')
meta

# Add secondary partitioning
meta <- applyPartitioning2(meta, 'tool_support')
meta

# Current partitioning
getPartitionings(meta)

```

## Sizing

```{r}
# Function for size calculation
psz <- function(ang) {
  power_centrality(ang)
}

# Sizes calculated by custom function
psz(meta[[length(meta)]])

# Test sizes calculated by the function
applySizing(meta, 'psz')

# Pregiven sizes
browseEntities(meta)[ ,c('object', 'wt')]

# Apply pregiven sizes
meta <- applySizing(meta, 'wt')
meta

# Current sizing
getSizing(meta)
```

## Alternation
```{r}
# Apply alternation
meta <- applyAlternation(meta)
meta

# Current alternation
getAlternation(meta)

# Remove alternation
meta <- removeAlternation(meta)
meta

# Current alternation
getAlternation(meta)
```

## Simplicity
```{r}
# Simple display of 10 biggest centers
applySimplicity(meta, n=10)
```

# Creating Order
```{r}
# For ordering vertex membership and sizing form a basis
getElements(meta)[ ,c('name', 'membership', 'size')]

# Analysis graph before applying order creation transformations
meta

# Try Scaling transformation
doScaling(meta, scaling=3)

# Average number of attributes
vl <- getElements(meta)[ ,c('name', 'membership', 'type')]
lapply(unique(vl$membership), function(m) {
  nent <- nrow(vl[vl$membership==m & vl$type=='entity', ])
  nattr <- nrow(vl[vl$membership==m & vl$type=='attribute', ])
  print(paste(m, 'mean number of attributes:', nattr/nent))}) -> NUL

# Try Symmetry transformation
doSymmetry(meta)

# Initiate Gradient transformation from SEQUENCE entity
meta <- doGradients(meta, 'SEQUENCE')
meta
```

# Highlighting
```{r}
# Vertex colouring by confuses highlighting  
meta <- removePartitioning2(meta)

# Highlight link attributes after applying alternation
meta <- applyAlternation(meta)
ida <- grep('>id|idx|step', getElements(meta)$name, value=TRUE)
meta <- applyHighlight(meta, ida)
meta

```

# Dynamics
*TODO: Archive and remove*
```{r}
# Facilitate reproducibility
set.seed(3)

# Generate sequences of 9 steps
n <- 9
steps <- 1:n

# Simulate the assembly sequence
asm <- unlist(lapply(steps, function(x) {
  rep(x, x + 1 + abs(rnorm(1, 0, 2)))
}))
s <- data.frame(cbind(type=rep('assembly', length(asm)), count=asm))

# Simulate the differentiation sequence
dif <- unlist(lapply(steps, function(x) {
  rep(x,  n * (n - x + abs(rnorm(1, 0, 2))))
}))
s <- rbind(s, cbind(type=rep('differentiation', length(dif)), count=dif))

# Output using ggplot2 graphics system
library(ggplot2)

col <-'darkblue'
lt <- 'dashed'
ckpt <- c('baseline', 'checkpoint 1', 'checkpoint 2')

# Build the barplot
ggplot(s, aes(x=count, fill=type)) + stat_count(width=0.8, position='dodge') +
  labs(x='steps', y='number of centers') + theme_grey(base_size=16) +
  theme(legend.position="top", legend.text=element_text(size=16)) +

  # Add checkpoints
  geom_vline(aes(xintercept=0.5), color=col, linetype=lt, size=1) +
  geom_text(aes(x=0.5, label=ckpt[1], y=100), hjust=-0.1, color=col, size=5) +
  geom_vline(aes(xintercept=3.5), color=col, linetype=lt, size=1) +
  geom_text(aes(x=3.5, label=ckpt[2], y=100), hjust=-0.1, color=col, size=5) +
  geom_vline(aes(xintercept=5.5), color=col, linetype=lt, size=1) +
  geom_text(aes(x=5.5, label=ckpt[3], y=100), hjust=-0.1, color=col, size=5)
```
