---
title: "Transformations"
output:
  html_document:
    fig_height: 8
    fig_width: 10
    highlight: tango
  word_document:
    fig_height: 8
    fig_width: 10
    highlight: tango
---

# Observations

```{r message=FALSE}
# Load common structural analysis functions
source('../strfa.R')

# TODO: Generate data based on analysis object definition?

# Load analysis data from a spreadsheet
suppressWarnings(library(readxl))
anobs <- read_excel('../data/meta.xlsx', sheet='trf')
anobs <- anobs[complete.cases(anobs), ]

# Structure of sample data
# str(anobs)

# Summary of properties
# table(anobs$property)

td <- analysis('Transformations demo', datarefl='anobs')
td <- applyTheme(td, 'minimalist')
```

# Structure generation
## <span style="font-variant:small-caps;">Reaching-Maturity</span> transformation

Idealised presentation of the analysis as a straight-forward sequence of steps. Actual progression might contain trees, cirles, loops, etc. 

Not based on data observations, as this describes overall organisation

```{r}
steps <- 1:10
asm <- c(2, 5, 8, 12, 9, 6, 8, 8, 7, 7)
dif <- c(29, 20, 23, 18, 15, 16, 10, 6, 8, 7)

# TODO: Labels and ticks inside the box?
par(cex=1.5, mar=c(4.4, 4.4, 1, 1))
plot(steps, asm, ylim=c(1,30), ylab='centres', xlab='steps', pch=0, col.lab='navy', col.axis='navy', cex.lab=1, cex.axis=0.9)
lines(steps, asm, lwd=2)
points(steps, dif, pch=2)
lines(steps, dif, lwd=2, col='darkgrey')
```

## <span style="font-variant:small-caps;">Presenting-Observations</span> transformation

```{r}
tdpo <- grow(td, 'OBS_1', depth=2)
tdpo <- applySeed(tdpo, 141)
tdpo <- applyPartitioning(tdpo, 'mbrp')
tdpo
```

## <span style="font-variant:small-caps;">Creative-Encapsulation</span> transformation

```{r}

# TODO: Pehaps show attribute grouping instead
# tdx <- grow(td, 'O1', depth=2)
# tdx <- group(tdx, 'OBSERVATIONS', c('O1', 'O2', 'O3'))
tdce <- group(tdpo, 'ANALYSIS', c('ENT_1', 'ENT_2'))
tdce <- applySeed(tdce, 537)
tdce

# New attempt
# tdx <- grow(td, 'G_ENTITY')
# tdx <- grow(tdx, 'G_ENTITY', attrs=T)
# tdx <- group(tdx, 'group_attr', c('G_ENTITY>attr3', 'G_ENTITY>attr4'))
# void(tdx, 'G_ENTITY2')
```

# Essential Global Properties
## <span style="font-variant:small-caps;">Randomization</span> transformation
```{r}
browseSeeds(tdpo)
```

## <span style="font-variant:small-caps;">Proper-Layout</span> transformation
```{r}
tdpl <- removePartitioning(tdpo)
browseLayouts(tdpl)
```

## <span style="font-variant:small-caps;">Proper-Theme</span> transformation
```{r}
browseThemes(tdce)
```

# Optional Global Properties
## <span style="font-variant:small-caps;">Partitioning</span> transformation
```{r}
# Custom function for partitioning
my_part_fun <- function(ang) {
  comm <- data.frame(as.character(V(ang)$name))
  comm$membership <- sub('.*\\_', '', comm[ ,1])
  comm
}

# Apply second partitioning
tdpt <- applyPartitioning2(tdpo, 'my_part_fun')
tdpt <- applySeed(tdpt, 141)
tdpt
```

## <span style="font-variant:small-caps;">Sizing</span> transformation
```{r}
tdsz <- applySizing(tdpo, 'wt')
tdsz
```

## <span style="font-variant:small-caps;">Simplicity</span> transformation

```{r}
applySimplicity(tdsz, n=2)
```

## <span style="font-variant:small-caps;">Alternation</span> transformation

```{r}
applyAlternation(tdsz)
```


# Structure polishing
## <span style="font-variant:small-caps;">Levels-of-Scale</span> transformation

```{r}
grow(td, 'LEVEL_1', depth=2)
```

## <span style="font-variant:small-caps;">Local-Symmetries</span> transformation

```{r}
grow(td, 'SYMMETRICAL_1', attrs=T)
```

## <span style="font-variant:small-caps;">Gradients</span> transformation

```{r}
tdx <- grow(td, 'G_FOCUS', depth=2, attrs=T)
tdx <- applyAlternation(tdx)
tdx <- applyLayout(tdx, 'layout_with_lgl')
applySeed(tdx, 299)
```

# Local Properties
## <span style="font-variant:small-caps;">Highlight</span> transformation

```{r}
applyHighlight(tdpo, 'OBS_3')
```
