---
title: "AA Module Overview"
output:
  html_document: default
  word_document: default
---
This is an overview of the AA module

```{r}
# Load analysis functions (TODO: still not happy with the name...)
source('../../wda.r')

# Load obeservations by ignoring error conditions
suppressWarnings(library(readxl))
tobs <- read.csv('../../../data/T24R10MB.csv', stringsAsFactors = FALSE)
tobs <- tobs[tobs$property!='ERROR', ]

aa <- analysis('Arrangement Architecture Overview', 'tobs')

# Observations made
str(tobs_wide)
```

## Context/Baseline

There are quite a few entities even without observed links:

```{r message=FALSE}
aa <- grow(aa, 'AA.ARRANGEMENT')
applyHighlight(aa, 'AA.ARRANGEMENT')

nrow(getElements(aa))

# Remove irrelevant centers
# voidList <- getCenters(lsov)$name
# baseList <- c(initList, 'CUSTOMER')
# baseList <- c(keepList, 'AA.PRODUCT','AA.PROPERTY','AA.ARRANGEMENT.ACTIVITY')
# lsov <- void(lsov, voidList[!voidList %in% baseList])
#lsov

# aaList <- c('AA.PRODUCT','AA.PROPERTY','AA.ARRANGEMENT.ACTIVITY')
# lsov <- grow(lsov, aaList, width=0)

# Keep track of each module separately
# lsov <- applyPartitioning(lsov, 'mbrp')
#lsov
```

## Value date

Add scanned links and divide into two parallel sequences by module

```{r}

# aasch <- void(lsov, 'LD.LOANS.AND.DEPOSITS', name='AA analysis')

# lsov <- grow(lsov, 'AA.ARRANGEMENT', width=0, attrs=TRUE)
# applySeed(aasch, 390)

# Separate analysis branch for LD
# ldsch <- void(lsov, 'AA.ARRANGEMENT', name='LD analysis')
# lsov <- grow(lsov, 'LD.LOANS.AND.DEPOSITS', width=0, attrs=TRUE)

# TODO: Remove irrelevant attributes
applyAlternation(lsov)
```

### AA module exloratory analysis

Number of tables in AA module:

> nrow(aaobs[!is.na(aaobs$mbrp), ])
[1] 2428

as it is not stricty normal... even more

Nonempty tables

> nrow(aaobs[!is.na(aaobs$mbrp) & aaobs$wt_volrec > 0, ])
[1] 1453

Linked to AA.ARRANGEMENT

> getCenters(lsov, ctype = 'entity')$name
 [1] "AA.ARRANGEMENT"               "AA.ARR.PRODUCT.ACCESS"        "AA.ARR.PROXY.PERMISSIONS"     "COMPANY"                     
 [5] "CURRENCY"                     "CUSTOMER"                     "AA.PRODUCT.GROUP"             "AA.PRODUCT.LINE"             
 [9] "AA.PRODUCT"                   "AA.PROPERTY"                  "AA.PRD.CAT.PRODUCT.ACCESS"    "AA.PRD.CAT.PROXY.PERMISSIONS"
[13] "AA.PRD.DES.PRODUCT.ACCESS"    "AA.PRD.DES.PROXY.PERMISSIONS" "AA.PRD.PRF.PRODUCT.ACCESS"    "AA.PRD.PRF.PROXY.PERMISSIONS"
[17] "EB.EXTERNAL.USER"      


Add scanned LD links

```{r}

# Add scanned LD links
lsov <- grow(lsov, c('LD.LOANS.AND.DEPOSITS'), ckpt='valdate')
lsov <- grow(lsov, c('STMT.ENTRY'), ckpt='baseline')

# After checking source tables remove irrelevant entities
valList <- c(baseList, 'LD.LOANS.AND.DEPOSITS', 'LD.SCHEDULE.DEFINE',
  'STMT.ENTRY', 'CUSTOMER', 'ACCOUNT')
lsov <- void(lsov, !(getCenters(lsov)$name %in% valList))
lsov


```

Add scanned AA links

# TODO: Determine why AA disbursement FT was not detected by scanning

```{r}
keepList <- getCenters(lsov, ctype='entity')$name

lsov <- grow(lsov, 'AA.ARRANGEMENT', ckpt='valdate')
# applyAlternation(aasch)

valList <- c(keepList, 'ACCOUNT', 'STMT.ENTRY', 'FUNDS.TRANSFER', 'AA.ARR.ACCOUNT')
valList <- c(valList, 'AA.ARR.PAYMENT.SCHEDULE', 'AA.SCHEDULED.ACTIVITY')
lsov <- void(lsov, !(getCenters(lsov)$name %in% valList))
lsov
```

## Repayment date

New and interesting AA.ACTIVITY.BALANCES>@ID|AA.ARRANGEMENT

Paid back Good Customer

Rescan after COB?

```{r}
# Separate analysis for good and bad loans
lsovg <- applySeed(lsov, 1)
lsovb <- applySeed(lsov, 101)
```
## Maturity date

EB.CONTRACT.BALANCES?

```{r}
# Separate analysis for good and bad loans
lsovg <- applySeed(lsovg, 2)
lsovb <- applySeed(lsovb, 102)
```

## Overdue repayment

```{r}
lsovb <- applySeed(lsovb, 103)
```

## Archival

Value tracking.... Statuses, balances?

```{r}
# Separate analysis for good and bad loans
lsovg <- applySeed(lsovg, 4)
lsovb <- applySeed(lsovb, 104)
```

## Conclusions

What can we conclude based on analysis (or in word only?)

```{r}
# Good loan sequence overview summary
sqmain <- c('baseline', 'value date', 'repayment date', 'maturity date')
sqmain2 <- c(sqmain, 'archival date')
plot(lsovg, main=sqmain2, steps=c(5,10,11,12,13), ncol=3)

# Bad loan sequence overview summary
sqmain <- c('baseline', 'value date', 'repayment date', 'maturity date')
sqmain2 <- c(sqmain, 'overdue repayment date', 'archival date')
plot(lsovb, main=sqmain2, steps=c(5,10,11,12,13,14), ncol=3)

```

