---
title: "Arrangement Architecture"
output:
  html_document: default
---
This is an overview of the AA module
```{r}
suppressWarnings(suppressPackageStartupMessages(library(tidyverse)))

# Load analysis functions (TODO: still not happy with the name...)
source('../../wda.r')

# Load observations
tobs <- read_csv('../../data/T24R18MB.csv', col_types = cols())

aa <- analysis('Arrangement Architecture', 'tobs')

```

# Overview
Many entities even without observed links:

```{r message=FALSE, fig.height=15, fig.width=15}
# Grow the big picture structure
aa <- grow(aa, 'AA.ARRANGEMENT') %>% applyPartitioning2('product')

applyHighlight(aa, 'AA.ARRANGEMENT')

# Total number of entities
nrow(elems <- getElements(aa))

# Products shown
unique(elems$membership2)
```

*TODO: legends to match products to colors*
Convert color hex code to color names
https://stat.ethz.ch/pipermail/r-help/2015-April/427663.html

*TODO: Fetch EB.PRODUCT*

# Product organisation

Branch away for going into details and later group in original sequence

Property can be set Mandatory or Optional in Product Group! (always fail in quiz)

```{r message=FALSE, fig.height=15, fig.width=15}
applyHighlight(aa, 'AA.PRODUCT.LINE') 
applyHighlight(aa, 'AA.PRODUCT.GROUP') 
applyHighlight(aa, 'AA.PRODUCT')
```

# Building blocks

AA.PROPERTY.CLASS, AA.PROPERTY

# Banking products

Product conditions are store in what tables?

# Lifecycle management
