---
title: "DATA CAPTURE OVERVIEW"
output:
  html_document: default
  word_document: default
---
This is a sequential business analysis of T24 security management system. It is based on R10 model bank data

Unlike other applications in T24 where a single transaction may create multiple accounting entries, DATA.CAPTURE operates by creating each accounting entry as a single transaction which, when combined with other transactions, form a ‘batch’. The following sections clarify the main components.
[Banking Framework > Data Capture > Setup ]

```{r}
# Load analysis functions (TODO: still not happy with the name...)
source('../../wda.r')

# Load obeservations by ignoring error conditions and scanned state changes
suppressWarnings(library(readxl))
tobs <- read.csv('../../../data/T24R10MB.csv', stringsAsFactors = FALSE)
tobs <- tobs[tobs$property != 'ERROR' & tobs$checkpoint == 'baseline', ]

# Initiate the analysis sequence
dc <- analysis('Data Capture Overview', 'tobs')
dc <- grow(dc, 'DATA.CAPTURE') %>%  grow('DATA.CAPTURE', attrs = T, depth = 0)

# Remove common fields
cf <- c('LOCAL.REF', 'OVERRIDE', 'RECORD.STATUS', 'CURR.NO', 'INPUTTER')
cf <- c(cf, 'DATE.TIME', 'AUTHORISER', 'CO.CODE', 'DEPT.CODE', 'AUDITOR.CODE', 'AUDIT.DATE.TIME')
dc <- void(dc, paste0('DATA.CAPTURE>', cf))

# Who cares about cheques: BC.SORT.CODE, CHEQUE.TYPE, CHEQUE.NUMBER

```

dc <- grow(sms, 'DATA.CAPTURE')
dc <- grow(dc, 'DATA.CAPTURE', attrs = T, depth = 0)
applyAlternation(dc)

# Defined structure
Training course T3SMS suggests that the likely primary centers are USER, OVERRIDE, DISPO.ITEMS, and EB.GC.CONSTRAINT entities

```{r fig.width=15, fig.height=10}
# Generate the initial big picture structure
entities <- browseEntities(sms)$object
prior_entities <- grep('USER|OVERRIDE|DISPO.|.GC.', entities, value = TRUE)
prior_centers <- c('USER', 'OVERRIDE', 'DISPO.ITEMS', 'EB.GC.CONSTRAINTS')
(sms <- grow(sms, prior_entities) %>% applyHighlight(prior_centers))

```

Cleanup based on module membership. Perhaps convert AA entities point to OVERRIDE into a group

```{r fig.width=15, fig.height=10}

sms <- applyPartitioning(sms, 'mbrp')

elems <- getElements(sms)
unique(elems$membership)

functional_modules <- elems[!elems$membership %in% c('AC', 'EB', 'ST'), 'name']
(sms <- void(sms, functional_modules))
```

Perhaps better not to remove these but to group later

```{r fig.width=15, fig.height=10}
# Remove not SMS related entities
usr_pref <- c('USER.ABBREVIATION', 'BROWSER.PREFERENCES', 'LANGUAGE', 'PRINTER.ID')
usr_ident <- c('TEC.PROFILE', 'REPORT.CONTROL', 'EB.LDAP.PARAMETER', 'EB.CHANNEL', 'EB.FILE.UPLOAD')
autom <- c('BATCH', 'EB.PHANTOM', 'OFS.SOURCE', 'TSA.SERVICE')
sys <- c('PGM.FILE', 'STANDARD.SELECTION')
non_sms_elems <- c(usr_pref, usr_ident, autom, sys)

(sms <- removePartitioning(sms) %>% void(non_sms_elems))


# OVERRIDE polishing
(sms <- grow(sms, 'OVERRIDE.CLASS'))

# DISPO polishing


# Global contraints polishing
grow(sms, tobs[grepl('EB.GC', tobs$object) & tobs$property == 'mbrp', 'object'])

```

# Observed structure

The DC.BATCH.CONTROL application is updated with the POSITION.TYPE record from the first entry of the batch which ensures all consecutive entries in the batch are of the same position type.
[R16AMR: Banking Framework > MultiGaap > Deal Processing Overview > DATA.CAPTURE]

```{r  fig.width=15, fig.height=10}
# USER polishing
proto_obs <- as_obs(list('PROTOCOL|USER>USER', 'type', 'scanned'))
(sms <- grow(sms, 'PROTOCOL', depth = 0, obs = proto_obs))

```

## Conclusions

What can we conclude based on analysis (or in word only?)

```{r fig.width=15, fig.height=10}

```

