---
title: "TDM"
output:
  html_document:
    number_sections: true
  word_document: default
---
```{r echo=FALSE}
# Load analysis functions (TODO: still not happy with the name... sba?)
source('../../wda.R')
source('../../obs.R')

suppressWarnings(library(readxl))
```
This is a reverse analysis of Temenos Data Migration Tool and Methodology for migrating data into and from T24. It should facilitate passing T3DMG-R17 certification exam without ever seeing the tool and with no training. Instead the analysis had to rely on observations extracted from somewhat vague tool and methodology documentation:

```{r}
# Load observations
dmo <- read_excel('../../data/tdm.xlsx')

# Initiate the analysis sequence
dm <- analysis('Temenos Data Migration Tool', 'dmo')
```

Different kind of entities have been observed and these should be differentiated in the structure. As of now, documents left out for simplicity sake. Analysis will be  quite detailed nevertheless and the alternating presentation of elements useful:

```{r}
# Partition to clusters by membership and turn on alternation property
dm <- applyPartitioning2(dm, 'mbrp') %>% applyAlternation

# Available entity types
table(browseData(dm)$mbrp)
```

# Mapping
What to upload or extract has to be specified. Possibly with the help of specific mapping programs

## Extract mapping
Start to grow the structure from central extract mapping table:

```{r fig.width=18, fig.height=18}
# Collect mapping centres
map_centres <- extract_centre <- 'DM.EXTRACTOR'

# Generate the structure
dm <- grow(dm, extract_centre) %>%
  grow(extract_centre, depth = 2, width = 0)

# Plot by higlighting the mapping centres
applyHighlight(dm, extract_centre)
```

Simplify the structure by removing non-actionable fields and by grouping similar attributes to avoid overly busy output:

```{r fig.width=20, fig.height=20}
# Fetch the extracting centre attribute names
dmea <- grep(paste0(extract_centre, '>'), getElements(dm)$name, value = TRUE)

# Remove descriptive or helper attributes
dm <- void(dm, grep('DESCRIPTION|SELECT', dmea, value = TRUE)) %>%
  
  # Merge the extract selection criteria attributes
  group('SELECTION', grep('COMP|FILE.TYPE|SEL\\.', dmea, value = TRUE)) %>%

  # Merge the extract specification attributes
  group('EXTRACT_SPEC', grep('OFS|DELIM|HEAD', dmea, value = TRUE)) %>%

  # Merge the extract field attributes
  group('EXTRACT_FIELDS', grep('FLD\\.|TRANS\\.', dmea, value = TRUE)) %>%

  # Merge data capture attributes
  group('DATA_CAPTURE', grep('LOCAL|DC|CAPTURE|TRANSACTION\\.', dmea, value = TRUE))
```

## Upload mapping
Add central upload mapping table to structure:

```{r fig.width=20, fig.height=20}
# Collect mapping centres
map_centres <- c(map_centres, upload_centre <- 'DM.MAPPING.DEFINITION')

# Generate the structure
dm <- grow(dm, upload_centre) %>%
  grow(upload_centre, depth = 2, width = 0)

# Plot by higlighting the mapping centres
applyHighlight(dm, upload_centre) %>% applySeed(277)
```

Group the attributes to avoid overly busy output:

```{r fig.width=20, fig.height=20}
# Fetch the upload mapping centre attribute names
dmda <- grep(paste0(upload_centre, '>'), getElements(dm)$name, value = TRUE)

# Remove descriptive or helper attributes
dm <- void(dm, grep('DESCRIPTION|SELECT', dmda, value = TRUE)) %>%

  # Merge the upload specification attributes
  group('UPLOAD_SPEC', grep('TYPE|OFS|DATA|DELIM|SEQ|RTN', dmda, value = TRUE)) %>%

  # Merge the upload field specification attributes
  group('UPLOAD_FIELDS', grep('ID|FIELD', dmda, value = TRUE))
```

## Mapping helpers
Manually populating mapping tables is a laborious undertaking. Some helper utilities seem to exist for supporting this:

* AUTO.DMD.CREATION service seems to be only utility which populates mapping tables directly
* TDM.DATA.STRUCTURE.EXTRACT extracts the structures of the traditional application.
* DM.AA.MAPPING extracts AA products with respective properties into AA.DMS.OUT directory
* DM.AA.EXTRACT and DE.MAPPING.EXTRACT are mentioned but their usage is unclear 

Expand mapping helpers which have data presentation:

```{r fig.width=22, fig.height=22}
map_helper_centres <- c('DM.AA.MAPPING', 'DM.AA.EXTRACT', 'DM.MAPPING.EXTRACT')

# Generate the structure
dm <- grow(dm, map_helper_centres) %>%
  grow(map_helper_centres, depth = 2, width = 0)

# Plot by higlighting the mapping centres
applyHighlight(dm, map_helper_centres) %>% applySeed(44)
```

Group the attributes to avoid overly busy output:

```{r fig.width=20, fig.height=20}
# Collect mapping centres
map_centres <- c(map_centres, map_helper_name <- 'MAPPING_HELPER')

# Group related elements
elems <- getElements(dm)$name

dm <- group(dm, map_helper_name, 
  elems[grepl('DM.AA|MAPPING.EXTRACT', elems) & !grepl('id|OUTPUT|APPL', elems)])
```

*TODO: group should preserve outgoing attributes if alternation is on*

## Mapping summary
Final structure for mapping phase identified with centres highlighted:

```{r fig.width=20, fig.height=20}
applyHighlight(dm, map_centres)
```

Linked elements not explained will be tackled in later phases

# Preprocessing
After mapping three preparatory steps should be completed before loading and extracting the data

## Record counting
Count records in target T24 system before migration by verifying DM.INFORMATION=SYSTEM record:

```{r fig.width=20, fig.height=20}
prep_centres <- 'RECORD_COUNTS'
count_centre <- 'DM.INFORMATION'

dm <- grow(dm, count_centre) %>%
  grow(count_centre, width = 0, depth = 2)

applyHighlight(dm, count_centre)
```

*TODO: DM.INFORMATION value SYSTEM not displayed*

Results should be tidied up for avoiding messy output:

```{r}
# Group count and remove non-actionable attributes
elems <- getElements(dm)$name

(count_attrs <- elems[grepl('^DM.INF.*COUNT', elems)])
(nact_attrs <- elems[grepl('DM.INFORMATION>', elems) & !grepl('COUNT|APPLICATION', elems)])
dm <- group(dm, 'XX.LIVE.NAU.HIS.COUNT', count_attrs) %>% void(nact_attrs)
```

## Directory structure
Create the directory structure (if not already present) for upload and extract files by verifying DM.PREREQUISITE records:
```{r fig.width=20, fig.height=20}
prep_centres <- c(prep_centres, dmp <- 'DM.PREREQUISITE')

# Generate the structure with file system objects
dm <- grow(dm, dmp) %>% grow(dmp, width = 0, depth = 2)

applyHighlight(dm, dmp)
```
Again, the results should be tidied up for avoiding messy output:
```{r fig.width=20, fig.height=20}
# Select elements from overly detailed structure for clean-up
elems <- subset(getElements(dm), grepl(paste0(prep_centres[2], '>'), name), c('name', 'label'))

(desc_attr <- elems[grep('DESCRIPTION|SELECT.LIST', elems$name), ])
(proc_attr <- elems[grep('PROCESS|RECONCILIATION', elems$name), ])
(file_attr <- elems[grep('CONV|TYPE', elems$name), ])
  
# Void descriptive,  group process control and file specification attributes
dm <- void(dm, desc_attr$name) %>%
  group('PROC.CONTROL', proc_attr$name) %>%
  group('FILE.SPEC', file_attr$name)
```

*TODO: Fix proc_attr print*

Group all counting elements to make space for new elements:
```{r}
count_elems <- c('DATA.MIG.COUNT', 'DATA.MIG.COUNT>id','DM.INFORMATION', 'XX.LIVE.NAU.HIS.COUNT')
dm <- group(dm, 'RECORD_COUNTS', count_elems)
```

## Service control
Verification of DM.PREREQUISITE records may also create service control records:

```{r fig.width=20, fig.height=20}
prep_centres <- c(prep_centres, dsc <- 'DM.SERVICE.CONTROL')

dm <- grow(dm, dsc, width = 0, depth = 2)

applyHighlight(dm, dsc)
```

Tidy up by group attributes again and output the structure after preparation steps:

```{r fig.width=20, fig.height=20}
elems <- subset(getElements(dm), grepl(paste0(prep_centres[3], '>'), name), c('name', 'label'))

(ctrl_attrs <- elems[grep('SERVER|USER|SESSIONS|STATUS|DSC|PROCESS', elems$name), ])
(log_attrs <- elems[grep('HIST|LOG|ERROR|DATE|STARTED|STOPPED|ELAPSED', elems$name), ])
dm <- group(dm, 'SERVICE.CONTROL', ctrl_attrs$name) %>% group('SERVICE.LOGS', log_attrs$name)
```

## Preparations summary

```{r fig.width=20, fig.height=20}
applyHighlight(dm, prep_centres)
```

# Migration

## Extracting

```{r fig.width=23, fig.height=23}

(dm <- grow(dm, c('DM.SERVICE.CONTROL', 'DM.SERVICE.CONTROL.CONCAT')) %>%
  grow('DM.SERVICE.SCHEDULER', depth = 2, width = 0))

group(dm, 'TSA', c('TSA.SERVICE', 'BATCH', 'TSA.WORKLOAD.PROFILE'))

#SERVICE_CONTROL group:
#'DM.SERVICE.CONTROL', 'DM.SERVICE.CONTROL.CONCAT>', 'DM.SERVICE.SCHEDULER>' 
 
#c('DM.SERVICE.CONTROL', 'DM.SERVICE.CONTROL.CONCAT', 'DM.SERVICE.SCHEDULER', 'TSA.SERVICE', 'BATCH', 'TSA.WORKLOAD.PROFILE'

#exclude: id, XX.CURRENT.DIRECTORY, XX.NEW.DIRECTORY, FLAT.FILE.DIR, ERROR.FILE.PATH, UPLOAD.COMPANY, ERROR.FILE.NAME


#elems <- getElements(dm)$name
#dm <- group(dm, map_helper_name,
#elems[grepl('DM.AA|MAPPING.EXTRACT', elems) & !grepl('id|OUTPUT|APPL', elems)])

```

DM.MAPPING.EXTRACT?

## Uploading
Mapping the source system data to target system and then attempting to upload

Verification of a DM.DATA.TRANSLATION record converts incoming file to a format suitable for mapping:

DMV directories created by DM.PREREQUISITE, so verification part of loading. Verify DATA.MAPPING.VERIFICATION to check the file first against DM.MAPPING.DEFINITION

```{r fig.width=20, fig.height=20}

# dm <- grow(dm, 'DM.DATA.TRANSLATION') %>% grow('DM.DATA.TRANSLATION', depth = 2, width = 0)

#(dm <- grow(dm, 'DATA.MAPPING.VERIFICATION'))

```

*TODO: Group DMD to tidy up*

Then DM.SERVICE.CONTROL. Group to TSS, BATCH, etc.

```{r fig.width=20, fig.height=20}
```

# Reconciliation


# Conclusion

*TODO: Entities observed as destination only not uncovered below*

Check if all entities covered:

```{r}
elems <- getElements(dm)
dm_entities <- elems[elems$type == 'entity','name']
obs_entities <- browseEntities(dm)$h_ent
obs_entities[!is.element(obs_entities, dm_entities)]
```

What can we conclude based on analysis

```{r fig.width=20, fig.height=20}
# (dmm <- removeAlternation(dm) %>% applySeed(133))
```

*TODO: Fix removeAlternation issue (RECORD_COUNTS must be be the reason*