---
title: "DM Tool"
output:
  html_document: default
  word_document: default
---


```{r}
# Load analysis functions (TODO: still not happy with the name... sba?)
source('../../wda.r')

# Observations

# TODO: Should make as_obs to extract facts presented in compact from
# TODO: Should be able to define links by presenting desc(ription)
tobs <- as_obs(list('DM.SERVICE.CONTROL>@ID|DM.MAPPING.DEFINITION', 'type', 'defined'))
tobs <- rbind(tobs, as_obs(list('DM.SERVICE.SCHEDULER>DM.SERVICE.ID|DM.SERVICE.CONTROL', 'type', 'defined')))

# Initiate the analysis sequence
dm <- analysis('DM Tool', 'tobs')

grow(dm, 'DM.SERVICE.CONTROL')
```



# Defined structure
Training course T3SMS suggests that the likely primary centers are USER, OVERRIDE, DISPO.ITEMS, and EB.GC.CONSTRAINT entities

```{r fig.width=15, fig.height=10}
# Generate the initial big picture structure
entities <- browseEntities(sms)$object
prior_entities <- grep('USER|OVERRIDE|DISPO.|.GC.', entities, value = TRUE)
prior_centers <- c('USER', 'OVERRIDE', 'DISPO.ITEMS', 'EB.GC.CONSTRAINTS')
(sms <- grow(sms, prior_entities) %>% applyHighlight(prior_centers))

```

Cleanup based on module membership. Perhaps convert AA entities point to OVERRIDE into a group

```{r fig.width=15, fig.height=10}

sms <- applyPartitioning(sms, 'mbrp')

elems <- getElements(sms)
unique(elems$membership)

functional_modules <- elems[!elems$membership %in% c('AC', 'EB', 'ST'), 'name']
(sms <- void(sms, functional_modules))
```

Perhaps better not to remove these but to group later

```{r fig.width=15, fig.height=10}
# Remove not SMS related entities
usr_pref <- c('USER.ABBREVIATION', 'BROWSER.PREFERENCES', 'LANGUAGE', 'PRINTER.ID')
usr_ident <- c('TEC.PROFILE', 'REPORT.CONTROL', 'EB.LDAP.PARAMETER', 'EB.CHANNEL', 'EB.FILE.UPLOAD')
autom <- c('BATCH', 'EB.PHANTOM', 'OFS.SOURCE', 'TSA.SERVICE')
sys <- c('PGM.FILE', 'STANDARD.SELECTION')
non_sms_elems <- c(usr_pref, usr_ident, autom, sys)

(sms <- removePartitioning(sms) %>% void(non_sms_elems))


# OVERRIDE polishing
(sms <- grow(sms, 'OVERRIDE.CLASS'))

# DISPO polishing


# Global contraints polishing
grow(sms, tobs[grepl('EB.GC', tobs$object) & tobs$property == 'mbrp', 'object'])

```

# Observed structure

The DC.BATCH.CONTROL application is updated with the POSITION.TYPE record from the first entry of the batch which ensures all consecutive entries in the batch are of the same position type.
[R16AMR: Banking Framework > MultiGaap > Deal Processing Overview > DATA.CAPTURE]

```{r  fig.width=15, fig.height=10}
# USER polishing
proto_obs <- as_obs(list('PROTOCOL|USER>USER', 'type', 'scanned'))
(sms <- grow(sms, 'PROTOCOL', depth = 0, obs = proto_obs))

```

## Conclusions

What can we conclude based on analysis (or in word only?)

```{r fig.width=15, fig.height=10}

```

