---
title: "TIF Overview"
output:
  html_document: default
---
This is an overview of Integration Framework T24 part

```{r}
suppressWarnings(suppressPackageStartupMessages(library(tidyverse)))

# Load analysis functions (TODO: still not happy with the name...)
source('../../wda.r')

# Load observations
tobs <- read_csv('../../data/T24R18MB.csv', col_types = cols())

# Initiate the sequence
tif <- analysis('Integration Framework Overview', 'tobs')
```

# Module overview
Inbound message out of T24 to middleware and vice versa

Grow the big picture structure from product observations:

```{r message=FALSE, fig.height=15, fig.width=15}
# Entities belonging to IF product
product_obs <- browseData(tif) %>% filter(product == 'IF')

# Generate initial structure separating products
(tif <- grow(tif, product_obs$object) %>%
  grow(product_obs$object, depth = 1, width = 0) %>%
  applyPartitioning2('product'))
```

# Flow definition
Event is a generic term for the notification which T24 emits when a business event occurs.

IF.EXIT.POINTS defines the hook, or API, in T24 to which an Event can be linked

XX<EXIT.POINT
XX>XX.INTEG.FLOW

Add observed link:
XX>XX.INTEG.FLOW|IF.INTEGRATION.FLOW.CATALOG

Version, Application, Component Service, TSA Service, Delivery Message

Flow Catalog (IF.INTEGRATION.FLOW.CATALOG)

Integration Flow. Defines the layout of an XML message which will leave T24 
when a business event occurs 

Enrichment (joins) is process of retrieving data which is stored in T24 for inclusion on the notification message 

A T24 table which contains details of all the Integration Flows which have been created by the system integrators. 

IF.INTEGRATION.FLOW.CATALOG>XX.EXIT.POINT|IF.EXIT.POINTS ???

Service Repository. Contains details of all the available component services, their 
operations, plus the data types and direction (in/out/inout) for 
each operation argument. 

IF.CALLBACK.IMPL.CATALOG catalogs the name of the local routines that implement callback APIs 

```{r message=FALSE, fig.height=15, fig.width=15}

```

# Event triggering
Store and Forward Table (IF.EVENTS.INTERFACE.TABLE)

- Store and forward table for event messages.
- Events stored here will be processed by a service or adapter 
- The processed events would get their timestamp updated 

IF.INTERFACE.TABLE>EVENT.TYPE|IF.INTEGRATION.FLOW.CATALOG ???

# Event polling
IF.CALLBACK.IMPL.CATALOG record SYSTEM only?

Event Batching (TSA.SERVICE>INTEGRATION.SERVICE)
Service that performs the delivery of the events which are stored 
in the store and forward table. 

Parameter Table (IF.INTEGRATION.SERVICE.PARAM)
Contains configuration parameters for the Integration Service 
Note — Integration Service is not required with custom adapters 

Transform table- IF.INTEGRATION.FLOW.TRANSFORM 
This table specifies the transformation (xslt) to be applied on a flow before it is delivered to a JMS queue 

grow(tif, 'IF.INTEGRATION.SERVICE.PARAM', depth = 1)

 *TODO: legends to match products to colors*
Convert color hex code to color names
https://stat.ethz.ch/pipermail/r-help/2015-April/427663.html

