---
title: "SMS OVERVIEW"
output:
  html_document: default
  word_document: default
---
This is a sequential business analysis of T24 security management system. It is based on R10 model bank data

```{r}
# Load analysis functions (TODO: still not happy with the name...)
source('../../wda.r')

# Load obeservations by ignoring error conditions and scanned state changes
suppressWarnings(library(readxl))
tobs <- read.csv('../../../data/T24R10MB.csv', stringsAsFactors = FALSE)
tobs <- tobs[tobs$property != 'ERROR' & tobs$checkpoint == 'baseline', ]

# Initiate the analysis sequence
sms <- analysis('SMS Overview', 'tobs')
```

# Defined structure
Training course T3SMS suggests that the likely primary centers are USER, OVERRIDE, DISPO.ITEMS, and EB.GC.CONSTRAINT entities

```{r fig.width=15, fig.height=10}
# Generate the initial big picture structure
entities <- browseEntities(sms)$object
prior_entities <- grep('USER|OVERRIDE|DISPO.|.GC.', entities, value = TRUE)
prior_centers <- c('USER', 'OVERRIDE', 'DISPO.ITEMS', 'EB.GC.CONSTRAINTS')
(sms <- grow(sms, prior_entities) %>% applyHighlight(prior_centers))

```

Cleanup based on module membership. Perhaps convert AA entities point to OVERRIDE into a group

```{r fig.width=15, fig.height=10}

sms <- applyPartitioning(sms, 'mbrp')

elems <- getElements(sms)
unique(elems$membership)

functional_modules <- elems[!elems$membership %in% c('AC', 'EB', 'ST'), 'name']
(sms <- void(sms, functional_modules))
```

Perhaps better not to remove these but to group later

```{r fig.width=15, fig.height=10}
# Remove not SMS related entities
usr_pref <- c('USER.ABBREVIATION', 'BROWSER.PREFERENCES', 'LANGUAGE', 'PRINTER.ID')
usr_ident <- c('TEC.PROFILE', 'REPORT.CONTROL', 'EB.LDAP.PARAMETER', 'EB.CHANNEL', 'EB.FILE.UPLOAD')
autom <- c('BATCH', 'EB.PHANTOM', 'OFS.SOURCE', 'TSA.SERVICE')
sys <- c('PGM.FILE', 'STANDARD.SELECTION')
non_sms_elems <- c(usr_pref, usr_ident, autom, sys)

(sms <- removePartitioning(sms) %>% void(non_sms_elems))


# OVERRIDE polishing
(sms <- grow(sms, 'OVERRIDE.CLASS'))

# DISPO polishing


# Global contraints polishing
grow(sms, tobs[grepl('EB.GC', tobs$object) & tobs$property == 'mbrp', 'object'])

```

# Observed structure

```{r  fig.width=15, fig.height=10}
# USER polishing
proto_obs <- as_obs(list('PROTOCOL|USER>USER', 'type', 'scanned'))
(sms <- grow(sms, 'PROTOCOL', depth = 0, obs = proto_obs))

```

## Conclusions

What can we conclude based on analysis (or in word only?)

```{r fig.width=15, fig.height=10}

```

