---
title: "SMS OVERVIEW"
output:
  html_document: default
  word_document: default
---
This is a sequential business analysis of T24 security management system (as identified by T3SMS training course). The analysis is based on R10 model bank data

```{r}
# Load analysis functions (TODO: still not happy with the name...)
source('../../wda.r')
source('../../obs.R')

# Load obeservations by ignoring error conditions and scanned state changes
suppressWarnings(library(readxl))
tobs <- read.csv('../../../data/T24R10MB.csv', stringsAsFactors = FALSE)

tobs <- tobs[tobs$property != 'ERROR' & tobs$checkpoint == 'baseline', ]

# Remove standard fields
sf <- '>LOCAL.REF$|>OVERRIDE$|>INPUTTER$|>AUTHORISER$|>DATE.TIME$|>CURR.NO$'
sf <- paste0(sf, '|>RECORD.STATUS$|>CO.CODE$|>DEPT.CODE$|>AUDITOR.CODE|>AUDIT.DATE.TIME$')
tobs <- tobs[!grepl(sf, tobs$object), ]

# Initiate the analysis sequence
sms <- analysis('SMS Overview', 'tobs')
```

# Defined structure
Training course suggests the naming conventions used and that the likely primary centers are USER, OVERRIDE, DISPO.ITEMS, and EB.GC.CONSTRAINT entities

```{r fig.width=15, fig.height=10}
# Generate the initial big picture structure
entities <- browseEntities(sms)$object
prior_entities <- grep('USER|OVERRIDE|DISPO.|.GC.', entities, value = TRUE)
prior_centers <- c('USER', 'OVERRIDE', 'DISPO.OFFICER', 'EB.GC.CONSTRAINTS')
(sms <- grow(sms, prior_entities) %>% applyHighlight(prior_centers))

```

Cleanup based on module membership as SMS affects all functional modules

```{r fig.width=15, fig.height=10}

sms <- applyPartitioning(sms, 'mbrp')

elems <- getElements(sms)
unique(elems$membership)

functional_modules <- elems[!elems$membership %in% c('EB', 'ST'), 'name']
(sms <- void(sms, functional_modules))
```

Remove items related to preferences, automation, and meta-items

*TODO: Perhaps convert AA entities pointing to OVERRIDE and non-sms items into groups*

```{r fig.width=15, fig.height=10}
# Remove not SMS related entities
usr_pref <- c('USER.ABBREVIATION', 'BROWSER.PREFERENCES', 'LANGUAGE', 'PRINTER.ID')
usr_ident <- c('TEC.PROFILE', 'REPORT.CONTROL', 'EB.LDAP.PARAMETER', 'EB.CHANNEL', 'EB.FILE.UPLOAD')
autom <- c('BATCH', 'EB.PHANTOM', 'OFS.SOURCE', 'TSA.SERVICE')
sys <- c('PGM.FILE', 'STANDARD.SELECTION')
non_sms_elems <- c(usr_pref, usr_ident, autom, sys)

(sms <- removePartitioning(sms) %>% void(non_sms_elems))
```

# User profiling

Branch off with USER related entities

```{r  fig.width=15, fig.height=10}
links <- getRelations(sms)$name
linked_entities <- gsub('USER\\||\\|USER', '', grep('^USER|USER$', links, value = TRUE))

entities <- getElements(sms)$name
(usr <- void(sms, entities[!entities %in% c('USER', linked_entities)]))
```

Observed items added

```{r  fig.width=15, fig.height=10}

proto_obs <- as_obs(list('PROTOCOL|USER>USER', 'type', 'scanned'))
(usr <- grow(usr, 'PROTOCOL', depth = 0, obs = proto_obs))


```

Attributes

*TODO: Group attributes*

```{r  fig.width=15, fig.height=10}

(usr <- grow(usr, c('USER', 'USER.SMS.GROUP'), attrs = TRUE, depth = 0) %>%
   applyLayout('layout_with_dh'))

```

# Overrides

```{r  fig.width=15, fig.height=10}
links <- getRelations(sms)$name
linked_entities <- gsub('OVERRIDE\\||\\|OVERRIDE', '', grep('^OVERRIDE|OVERRIDE$', links, value = TRUE))

entities <- getElements(sms)$name
(ovd <- void(sms, entities[!entities %in% c('OVERRIDE.CLASS', linked_entities)]))

entities <- getElements(ovd)$name
(ovd <- grow(ovd, grep('OVERRIDE', entities, value = TRUE), attrs = TRUE, depth = 0))

```

# Dispo control

```{r  fig.width=15, fig.height=10}
entities <- getElements(sms)$name
(dsp <- void(sms, grep('DISPO', entities, value = TRUE, invert = TRUE)) %>%
  grow(c('DISPO.OFFICER')))

(dsp <- grow(dsp, c('DISPO.OFFICER', 'DISPO.ITEMS', 'DISPO.PARAMETER'), attrs = T, depth = 0))

```

# Global constraings

```{r  fig.width=15, fig.height=10}

# Global contraints polishing
grow(sms, tobs[grepl('EB.GC', tobs$object) & tobs$property == 'mbrp', 'object'])

```

## Conclusions

What can we conclude based on analysis (or in word only?)

```{r fig.width=15, fig.height=10}

```

