---
title: "Overview"
output:
  html_document: default
  word_document:
    fig_height: 12
    fig_width: 8
    highlight: tango
---
It is quite common for a professional analyst to find him or herself facing a new complex software system and to be expected to make sense of it quickly. There may be a lot of documentation to go through and relevant training sessions, but self-study can complement this very well, as illustrated by this example

We have used a dedicated program for extracting basic structural information from current T24 installation and loaded its output into a spreadsheet:

```{r message=FALSE}
# Load observations
suppressWarnings(library(readxl))
tobs <- read_excel('../../data/t24.xlsx')

# Load transformation functions and start the sequence
source('../strfa.R')
sov <- analysis('System Overview', 'tobs')
```

It is convenient to collect the source data in a long format (in this analysis there are 86543 individual object-property-value observations in our disposal), but for analysis the data in a wide format (produduced by *analysis* function) is more suitable:

```{r message=FALSE}
# Observations in a long format
str(tobs, strict.width='cut', width=70)

# Observations in a wide format
str(tobsw[ ,1:(ncol(tobsw)-3)], strict.width='cut', width=70)
```

**Big picture.** Our first attempt to explore the structure highlights the challenges in doing that. There are just too many items to grasp:

```{r}
# Create a structure comprised of all entities
entities <- browseEntities(sov)$object
sov <- grow(sov, entities, width=0)
# load('sov2.dat')
sov
```

**Sizing and Simplifying.** Not should all entities be treated equally.We can try to identify what makes the difference based on some metric like size in bytes, connectedness, or completeness. Below a simple record count *wt_numrec* is used for this purpose:

```{r}
# Pregiven sizing based on record counts
sov <- applySizing(sov, 'wt_numrec')

# Identify main centers
sov <- applySimplicity(sov, n=25)
sov
```

**Void and Partitioning.** Visualisation indicates that many entities have no connections defined. For more concrete analysis tasks, these can be discovered by scanning records for links. Also, it is quite common for a T24 installation to have a lot of tables created with no use. These can be filtered out and entities categorised by modules to which underlying tables are assigned to:

```{r}
# Remove entities with zero records
centers <- getCenters(sov)
zeroCenters <- centers[centers$size==0,'name']
sov <- void(sov, centers=zeroCenters)

# TODO: Would be great to see module elements clustered
# Partition the entities by module
sov <- applyPartitioning(sov, 'mbrp_module')
sov
```

**Grouping.** Individual connections and relative positioning are too detailed in this context. We can make the display more compact by just grouping the entities by their membership and by preserving their numeric (sizing) importance. This gives us quite comprehensive overview of the system:

```{r}
# Group by membership attribute
sov <- group(sov, by='membership')

# Membership detection error analysis is not a concern
errc <- c('ERR_NO_PRODUCT_IN_PGM.FILE', 'ERR_NOT_IN_PGM.FILE')
sov <- void(sov, centers=errc)
sov
```

**Polishing.** We can further elaborate the presentation by attempting to choose most suitable layout algorithm and experiment with randomization settings for the graph. Although for the latter, changing randomisation settings has little effect:

```{r}
browseLayouts(sov)
sov <- applyLayout(sov, 'layout_components')
sov

# TODO: Initial seed pregiven to ensure reproducibility
browseSeeds(sov)
sov <- applySeed(sov, 201)
sov
```

**Concluding.** We seem to have a somewhat typical installation where the customer’s business is comprised mostly by lending products best handled by simple accounts (AC) with significant amount of custom local development (EB). We may also notice that built in reporting/accounting (RE) module is heavily utilised.

To summarise, we plot the most characteristic sequence steps. We could have also chosen to store the analysis code and data for later retrieval:

```{r}
sqmain <- c('all entities', 'sizing and simplifying', 'void and partitioning')
sqmain <- c(sqmain, 'grouping and polishing')
signoff(sov, thumb_seq=c(2, 4, 6, 10), thumb_narr=sqmain)
```

