---
title: "T24R18MB fetching"
output: html_document
---

Access only through Browser

```{r}
suppressWarnings(suppressPackageStartupMessages(library(tidyverse)))
```

# STANDARD.SELECTION
Create ENQUIRY:

* FILE.NAME = STANDARD.SELECTION
* SELECTION = UNLIKE NOFILE...
* OPERATION.1 = FILE.NAME
* OPERATION.2 = SYS.FIELD.NAME
* OPERATION.3 = SYS.REL.FILE
* OPERATION.4 = SYS.FIELD.NO

Create ENQUIRY.REPORT, REPORT.CONTROL. Generate report and copy via clipboard to text file

```{r}
col_names <- c('application', 'field', 'link', 'field_no')
(ss <- read_delim('../../data/raw/T24R18MB_SS.txt', '\t', escape_double = FALSE,
  col_names = col_names, col_types = cols(), trim_ws = TRUE))

# Remove strange entries with no field populated
nrow(ss <- ss[!is.na(ss$field), ])

# Populate application field
ss <- fill(ss, application)

# Remove @ID duplicates
nrow(ss <- ss[!(ss$field_no == 0 & ss$field != '@ID'), ])

# Remove unwanted (most of the time) service and audit fields
service_fields <- c('LOCAL.REF', 'OVERRIDE', 'RECORD.STATUS', 'CURR.NO')
audit_fields <- c('INPUTTER', 'DATE.TIME', 'AUTHORISER', 'CO.CODE', 'DEPT.CODE', 'AUDITOR.CODE', 'AUDIT.DATE.TIME')
nrow(ss <- ss[!ss$field %in% c(audit_fields, service_fields), ])

# Reserved fields removal pattern
r1 <- paste0('RESERVE\\.', 1:10, collapse = '|')
reserved_fields <- paste('^RESERVED', r1, sep = '|')

# Lots of poissible placeholders for future fields
as.vector(as.matrix(unique(ss[grepl('^RES', ss$field) & !grepl(reserved_fields, ss$field), 'field'])))

# Remove most prevalent reserved fields
nrow(ss <- ss[!grepl(reserved_fields, ss$field), ])
```

# PGM.FILE
Create ENQUIRY:

* FILE.NAME = PGM.FILE
* SELECTION = TYPE NE B M S
* OPERATION.1 = @ID
* OPERATION.2 = TYPE
* OPERATION.3 = PRODUCT

Run and save results to csv  file

```{r}
(pf <- read_csv('../../data/raw/T24R18MB_PGM.csv', col_types = cols()))

nrow(pf <- pf[!complete.cases(pf), ])
```

# Observations

```{r}
ss$object <- paste(ss$application, ss$field, sep = '>')
ss$object <- ifelse(is.na(ss$link), ss$object, paste(ss$object, ss$link, sep = '|'))

ss$property <- ifelse(is.na(ss$link), NA, 'type')
ss$value <- ifelse(is.na(ss$link), NA, 'strong')

obs <- ss[ ,c('object', 'property', 'value')]

View(obs)
```

