---
title: "T24 Model Bank structure fetching"
output: html_document
---

Access only through Browser

```{r}
suppressWarnings(suppressPackageStartupMessages(library(tidyverse)))
```

# STANDARD.SELECTION
Create ENQUIRY:

* FILE.NAME = STANDARD.SELECTION
* SELECTION = UNLIKE NOFILE...
* OPERATION.1 = FILE.NAME
* OPERATION.2 = SYS.FIELD.NAME
* OPERATION.3 = SYS.REL.FILE
* OPERATION.4 = SYS.FIELD.NO

Create ENQUIRY.REPORT, REPORT.CONTROL. Generate report and copy via clipboard to text file

```{r}
col_names <- c('application', 'field', 'link', 'field_no')
(ss <- read_delim('../../data/raw/T24R18MB_SS.txt', '\t', escape_double = FALSE,
  col_names = col_names, col_types = cols(), trim_ws = TRUE))
```

Remove unwanted (most of the time) fields:

```{r}
service_fields <- c('LOCAL.REF', 'OVERRIDE', 'RECORD.STATUS', 'CURR.NO')
audit_fields <- c('INPUTTER', 'DATE.TIME', 'AUTHORISER', 'CO.CODE', 'DEPT.CODE', 'AUDITOR.CODE', 'AUDIT.DATE.TIME')
(ss <- ss[!ss$field %in% c(audit_fields, service_fields), ])

# Reserved fields removal pattern
r1 <- paste0('RESERVE\\.', 1:10, collapse = '|')
reserved_fields <- paste('^RESERVED', r1, sep = '|')

# Lots of poissible placeholders for future fields
as.vector(as.matrix(unique(ss[grepl('^RES', ss$field) & !grepl(reserved_fields, ss$field), 'field'])))

# Remove most prevalent reserved fields
(ss <- ss[!grepl(reserved_fields, ss$field), ])
```

Populate application:

https://stackoverflow.com/questions/10554741/fill-in-data-frame-with-values-from-rows-above

```{r}

s1 <- ss[1:19, 'application']
s2 <- ss[2:20, 'application']
ifelse(is.na(s2), s1, s2)

```

# PGM.FILE
Create ENQUIRY:

* FILE.NAME = PGM.FILE
* SELECTION = TYPE NE B M S
* OPERATION.1 = @ID
* OPERATION.2 = TYPE
* OPERATION.3 = PRODUCT

Run and save results tp csv  file

# Output observations
