---
title: "Case Study Data"
output:
  html_document: default
  word_document:
    highlight: tango
---
We have run a data collection program in the test system. The program fetched the information on the system structure from relevant structure definition files (e.g. STANDARD.SELECTION, PGM.FILES) and took random samples from all data files (up to 30 samples per file). The data observations were loaded into a spreadsheet for initial correctness checking:

```{r}
# Load data observations
suppressWarnings(library(readxl))
t24obs <- read_excel('../data/t24.xlsx')

# TODO: Remove after fixing source data
for (idx in 1:nrow(t24obs)) {
  
  if (t24obs[idx,'property']=='wt_numattr') {
    numattr <- as.integer(t24obs[idx,'value'])
  }

  if (t24obs[idx,'property']=='wt_fillrec') {
    fillrec <- as.integer(t24obs[idx,'value'])
    if (fillrec==0) {
      t24obs[idx,'value'] <- NA
    } else {
      if (numattr > 0) {
        t24obs[idx,'value'] <- as.integer(t24obs[idx,'value'])/numattr
      }
    }
  }
}

# Observations data frame structure
str(t24obs, strict.width='cut', width=70)

```
Attempting to anticipate every possible property and statistic which might be needed in later analysis is both wasteful and unrealistic. Therefore, the observations were arranged in flexible object-property-value format. For case study analyses the following properties and samples were collected:

```{r}
# Summary of object properties observed
table(t24obs$property)

# Sample observations of each property
set.seed(123)
sobs <- t(sapply(unique(t24obs$property), function(x) {
  sobs <- t24obs[t24obs$property==x,]; sobs[sample(1:nrow(sobs), 1), ] }))
print(as.data.frame(sobs), row.names=FALSE)

```

For making sense of the data is reasonable to convert it to a “wide format”. Below this is achieved by using specifically developed helper functions which will be discussed later. Please also note the total number of observations:

```{r}
# Load analysis functions and initialize the sequence
source('strfa.R')
t24 <- analysis('t24expl', 't24obs')

# Retrieve the data in wide format
obsw <- browseData(t24)
str(obsw, give.attr=FALSE, strict.width='cut', width=70)
```

We will build a summary plot (a “dashboard”) to visualize the essential aspects of a particular system, consisting of five sub-plots.

Firstly, modularization can provide us a first glimpse to the whole system. We will present the discovered modules in a barplot, each module’s height reflecting the number of tables belonging to a module and width the record count. Logarithmic presentation of the latter should be considered, also we have skipped all the historical records (e.g. every contract change might be stored as a new record, thus in a lifetime the contract may have hundreds of copies). Distinction has been made between core tables (created by the vendor) and local tables. Here the volume of the latter is small, but the ratio may vary drastically between sites, depending on the customer wishes and the age of the system (older installations tend to have more local developments):

```{r}
m <- obsw[!is.na(obsw$mbrp_module), ]

# Mark unknown items
m[grepl('ERR_', m$mbrp_module), 'mbrp_module'] <- '?'

# Record counts by module
mrec <- aggregate(wt_numrec~mbrp_module, m, sum)
mrec$width <- round(log10(1+mrec$wt_numrec))
colnames(mrec) <- c('module', 'numrec', 'lognrec')

# Core and local file counts by module
mcore <- data.frame(table(m[m$mbrp_localcore=='core','mbrp_module']))
mlocal <- data.frame(table(m[m$mbrp_localcore=='local','mbrp_module']))
mtab <- merge(mcore, mlocal, by='Var1', all.x=TRUE)
colnames(mtab) <- c('module', 'corentab', 'localntab')

# Modularization plot data
modp <- merge(mtab, mrec, by='module')
modp[is.na(modp)] <- 0
modp
```

Number of records and attributes might be indicative metrics, but these can be also quite deceptive. The same can be said about the data size and completeness (fill rate) information. On the other hand, we could have utilized more advanced metrics like  diversity of values.

Now we have prepared all the data for the summary plot (some formatting code will be omitted):

```{r echo=FALSE}
# Plot parameters
par(mar=c(4,4,3,1), oma=c(1,1,2,0), cex.lab=1)
layout(matrix(c(1,2,4,1,3,5), nrow=3))

# Modularization plot
m <- t(modp)
main <- 'Modularization'
xlab <- 'module codes (?: unknown; bar width: number of records (log10)'
ylab <- 'number of files (tables)'
barplot(m[c('corentab', 'localntab'), ], names=m['module', ], 
  width=as.numeric(m['lognrec', ]), space=0, main=main, cex.names=0.8,
  xlab=xlab, ylab=ylab, legend=c('core','local'))

# Number of records and attributes plots
ylab <- 'frequency'
with(obsw, {
  main <- 'Number of Records'
  xlab <- 'records per table [log10(1+wt_numrec)]'
  hist(log10(1+wt_numrec), breaks=20, main=main, xlab=xlab, ylab=ylab)
  ntab <- sum(as.numeric(m[c('corentab', 'localntab'), ]))
  text(4, 1000, paste('Total number of tables:', ntab))
  text(4, 800, paste('Total number of records:', sum(wt_numrec, na.rm=TRUE)))
  
  main <- 'Number of Attributes'
  xlab <- 'attributes per record [wt_numattr]'
  hist(wt_numattr, breaks=20, main=main, xlab=xlab, ylab=ylab)
  mna <- round(mean(wt_numattr, na.rm=TRUE))
  text(120, 450, paste('Mean number of attributes:', mna))
})

# Sizing plot
cb <- c(0, 20, 50, 100, 500, seq(1000, 7000, by=1000))
volrec <- obsw[!is.na(obsw$wt_volrec), c('wt_volrec','wt_numrec')]
vr <- cut(volrec$wt_volrec, breaks=cb, include.lowest=TRUE)
vr <- table(vr)/length(vr)*100

wt_volattr <- obsw[!is.na(obsw$wt_volattr), 'wt_volattr']
va <- cut(wt_volattr, breaks=cb, include.lowest=TRUE)
va <- table(va)/length(va)*100

xlab <- 'item size (bytes) [wt_volrec; wt_volattr]'
ylab <- 'percent of items'
leg <- c('records','attributes')
barplot(rbind(vr, va), beside=TRUE, main='Sizes',
  xlab=xlab, ylab=ylab, legend=leg)

totsize <- round(sum(volrec$wt_volrec*volrec$wt_numrec)/1024/1024)
text(20, 50, paste('Total data size:', totsize, 'MB'))

# Completeness plot
wt_fillrec <- obsw[!is.na(obsw$wt_fillrec), 'wt_fillrec']*100
fr <- cut(wt_fillrec, breaks=seq(0, 100, by=10), include.lowest=TRUE)
fr <- table(fr)/length(fr)*100

wt_fillattr <- obsw[!is.na(obsw$wt_fillattr), 'wt_fillattr']*100
fa <- cut(wt_fillattr, breaks=seq(0, 100, by=10), include.lowest=TRUE)
fa <- table(fa)/length(fa)*100

xlab <- 'completeness percentage [wt_fillrec; wt_fillattr]'
barplot(rbind(fr, fa), beside=TRUE, main='Completeness',
  xlab=xlab, ylab=ylab, legend=leg)

mnc <- round(mean(wt_fillattr, na.rm=TRUE))
text(18, 30, paste0('Mean completeness: ', mnc, '%'))

mtext("Summary of Live Data Observations", outer=TRUE, cex=1.3)
```

