---
title: "Lending Product Comparison"
output:
  html_document: default
  word_document: default
---
This is the analysis/comparison of different loan scheduling mechanisms

TODO: Part of word doc. Loans are quite complex financial instruments. Lifecycle in decades. Various possible events. Simplified coverage here

Big questions: 
-what is connected to what?
-How relavant values change over time?
-What causes values to change?

We have run the program to extract the structure from sample system into a csv file. We run it on each checkpoint, to capture the changes over time

```{r}
# Load analysis functions (TODO: still not happy with the name...)
source('strfa.R')

# Initialise the analysis sequence
lsobs <- read.csv('../data/T24R10MB.csv', stringsAsFactors=FALSE, na.strings='')
lsov <- analysis('Loan scheduling overview', 'lsobs')

# Observations made
str(lsobsw)
```

## Context/Baseline

There are too many edges shown and most of them are not particularly useful in this context. Remove these and replace with connections based on record scan

Two clusters linked with CUSTOMER

```{r message=FALSE}

# Initial center candidates
initList <- c('LD.LOANS.AND.DEPOSITS', 'AA.ARRANGEMENT')
lsov <- grow(lsov, initList, ckpt='baseline')
# lsov <- applyLayout(lsov, layout='layout_components')
lsov

# Remove irrelevant centers
voidList <- getCenters(lsov)$name
baseList <- c(initList, 'CUSTOMER')
# baseList <- c(keepList, 'AA.PRODUCT','AA.PROPERTY','AA.ARRANGEMENT.ACTIVITY')
lsov <- void(lsov, voidList[!voidList %in% baseList])
lsov

# aaList <- c('AA.PRODUCT','AA.PROPERTY','AA.ARRANGEMENT.ACTIVITY')
# lsov <- grow(lsov, aaList, depth=0)

# Keep track of each module separately
lsov <- applyPartitioning(lsov, 'mbrp')
lsov
```

## Value date

Add scanned links and divide into two parallel sequences by module

```{r}

# aasch <- void(lsov, 'LD.LOANS.AND.DEPOSITS', name='AA analysis')

# lsov <- grow(lsov, 'AA.ARRANGEMENT', depth=0, attrs=TRUE)
# applySeed(aasch, 390)

# Separate analysis branch for LD
# ldsch <- void(lsov, 'AA.ARRANGEMENT', name='LD analysis')
# lsov <- grow(lsov, 'LD.LOANS.AND.DEPOSITS', depth=0, attrs=TRUE)

# TODO: Remove irrelevant attributes
applyAlternation(lsov)
```

### AA module exloratory analysis

Number of tables in AA module:

> nrow(aaobs[!is.na(aaobs$mbrp), ])
[1] 2428

as it is not stricty normal... even more

Nonempty tables

> nrow(aaobs[!is.na(aaobs$mbrp) & aaobs$wt_volrec > 0, ])
[1] 1453

Linked to AA.ARRANGEMENT

> getCenters(lsov, ctype = 'entity')$name
 [1] "AA.ARRANGEMENT"               "AA.ARR.PRODUCT.ACCESS"        "AA.ARR.PROXY.PERMISSIONS"     "COMPANY"                     
 [5] "CURRENCY"                     "CUSTOMER"                     "AA.PRODUCT.GROUP"             "AA.PRODUCT.LINE"             
 [9] "AA.PRODUCT"                   "AA.PROPERTY"                  "AA.PRD.CAT.PRODUCT.ACCESS"    "AA.PRD.CAT.PROXY.PERMISSIONS"
[13] "AA.PRD.DES.PRODUCT.ACCESS"    "AA.PRD.DES.PROXY.PERMISSIONS" "AA.PRD.PRF.PRODUCT.ACCESS"    "AA.PRD.PRF.PROXY.PERMISSIONS"
[17] "EB.EXTERNAL.USER"      


Add scanned LD links

```{r}

# Add scanned LD links
lsov <- grow(lsov, c('LD.LOANS.AND.DEPOSITS'), ckpt='valdate')
lsov <- grow(lsov, c('STMT.ENTRY'), ckpt='baseline')

# After checking source tables remove irrelevant entities
valList <- c(baseList, 'LD.LOANS.AND.DEPOSITS', 'LD.SCHEDULE.DEFINE',
  'STMT.ENTRY', 'CUSTOMER', 'ACCOUNT')
lsov <- void(lsov, !(getCenters(lsov)$name %in% valList))
lsov


```

Add scanned AA links

# TODO: Determine why AA disbursement FT was not detected by scanning

```{r}
keepList <- getCenters(lsov, ctype='entity')$name

lsov <- grow(lsov, 'AA.ARRANGEMENT', ckpt='valdate')
# applyAlternation(aasch)

valList <- c(keepList, 'ACCOUNT', 'STMT.ENTRY', 'FUNDS.TRANSFER', 'AA.ARR.ACCOUNT')
valList <- c(valList, 'AA.ARR.PAYMENT.SCHEDULE', 'AA.SCHEDULED.ACTIVITY')
lsov <- void(lsov, !(getCenters(lsov)$name %in% valList))
lsov
```

## Repayment date

New and interesting AA.ACTIVITY.BALANCES>@ID|AA.ARRANGEMENT

Paid back Good Customer

Rescan after COB?

```{r}
# Separate analysis for good and bad loans
lsovg <- applySeed(lsov, 1)
lsovb <- applySeed(lsov, 101)
```
## Maturity date

EB.CONTRACT.BALANCES?

```{r}
# Separate analysis for good and bad loans
lsovg <- applySeed(lsovg, 2)
lsovb <- applySeed(lsovb, 102)
```

## Overdue repayment

```{r}
lsovb <- applySeed(lsovb, 103)
```

## Archival

Value tracking.... Statuses, balances?

```{r}
# Separate analysis for good and bad loans
lsovg <- applySeed(lsovg, 4)
lsovb <- applySeed(lsovb, 104)
```

## Conclusions

What can we conclude based on analysis (or in word only?)

```{r}
# Good loan sequence overview summary
sqmain <- c('baseline', 'value date', 'repayment date', 'maturity date')
sqmain2 <- c(sqmain, 'archival date')
plot(lsovg, main=sqmain2, steps=c(5,10,11,12,13), ncol=3)

# Bad loan sequence overview summary
sqmain <- c('baseline', 'value date', 'repayment date', 'maturity date')
sqmain2 <- c(sqmain, 'overdue repayment date', 'archival date')
plot(lsovb, main=sqmain2, steps=c(5,10,11,12,13,14), ncol=3)

```

